Supplementary Materials: Probing the Deuteron at Very Large Internal Momenta

### 2020-10-19 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/ms.tex
updated supp

carried out at Jefferson Lab (JLab) and Berkeley National Lab (BNL). In these experiments nucleon momenta up to $p_{\mathrm{r}}\sim1$ GeV/c have been probed and recoil momentum distributions

@@

Recoil momenta up to $p_{\mathrm{r}}\sim1$ GeV/c have also been probed in a $^{3}\mathrm{He}(e,e'p)$ experiment \cite{PhysRevLett.94.082305,PhysRevLett.94.192302} but at a relatively low momentum transfer of 1.5 (GeV/c)$^{2}$ and at a kinematic region
(Bjorken $x_{\mathrm{Bj}}\sim1$) where the cross section is dominated by final state interactions.\\

@@

simulation program, SIMC \cite{PhysRevC.64.054610} (see Supplemental Material). Additional $^{1}\mathrm{H}(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization, 

@@

the systematic uncertainties due to proton loss in HMS ($0.49 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$), which were the same for every setting,
to define the overall normalization uncertainty ($\leq$ 4.2$\%$).\\

@@

The total uncertainty was defined as the quadrature sum of the normalization ($\leq$ 4.2$\%$), kinematic ($\leq$ 6.5$\%$) and statistical ($\sim20-30\%$ on average) uncertainties.\\

@@

$E_{\mathrm{f}}$ is the final proton energy, $f_{\mathrm{rec}}\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$
is a recoil factor obtained by integrating over the missing energy of the bound state in the 6-fold differential cross section where $E_{\mathrm{r}}$ is the neutron recoil energy, and $\sigma_{\mathrm{cc1}}$ is the

@@

The MS calculations used the FF parametrization of Ref. \cite{PhysRevC.70.068202} while the JML calculations used the conventional dipole parametrization for the proton and neutron magnetic FF, the Galster \cite{Galster:1971} parametrization
for the neutron electric FF, and the results from the Hall A experiment of Ref. \cite{PhysRevLett.88.092301} for the proton electric FF parametrization. The JVO calculations used two different FF parametrizations (GKex05 \cite{PhysRevC.66.045501}, AMT \cite{PhysRevC.76.035205}) where a difference of $\sim5.8-6.6 \%$ was found between the respective
JVO reduced cross sections. Figure \ref{fig:fig1} shows the results using only the GKex05 parametrization. \\

@@

  Insets: A blowup of the corresponding subfigure in the range $p_{\mathrm{r}}=0 - 0.7$ GeV/c.}

@@

%---include references that are not mentioned in the main text
%---but are included in the supplemental material
%---cite supp. material as follows:  (See Supplemental Material) after description of the topic being discussed.
\nocite{COSY}
\nocite{barlow2002systematic}
\nocite{barlow2017}

>>>>

carried out at Jefferson Lab (JLab) \cite{PhysRevLett.113.022501,PhysRevLett.122.172502,PhysRevLett.124.212501} and Brookhaven National Lab (BNL) \cite{PhysRevLett.97.162504}. In these experiments missing momenta up to $\sim1$ GeV/c have been probed and missing momentum distributions

@@

Missing momenta up to $\sim1$ GeV/c have also been probed in a $^{3}\mathrm{He}(e,e'p)$ experiment \cite{PhysRevLett.94.082305,PhysRevLett.94.192302} but at a relatively low momentum transfer of 1.5 (GeV/c)$^{2}$ and at a kinematic region
(Bjorken $x_{\mathrm{Bj}}\sim1$) where the cross section is dominated by final state interactions. Due to FSI effects, the measurement of a certain missing momentum does not yet guarantee that the initial
bound nucleon with the same momentum is being measured.\\

@@

simulation program, SIMC \cite{PhysRevC.64.054610}. Additional $^{1}\mathrm{H}(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization, 

@@

the systematic uncertainties due to proton loss in HMS ($0.49 \%$), total live time ($3.0 \%$), total charge ($2.0\%$), target wall contributions ($\leq2.9\%$) and spectrometer acceptance ($1.4\%$),  which were the same for every setting,
to define the overall normalization uncertainty ($\leq5.3\%$).\\

@@

The total uncertainty was defined as the quadrature sum of the normalization ($\leq$ 5.3$\%$), kinematic ($\leq$ 6.5$\%$) and statistical ($\sim20-30\%$ on average) uncertainties.\\

@@

($E_{\mathrm{f}}, p_{\mathrm{f}}$) are the final proton energy and momentum, respectively, $f_{\mathrm{rec}}$ %\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$
is a recoil factor \cite{cyero_phdthesis} obtained by integrating over the binding energy of the bound state in the 6-fold differential cross section and $\sigma_{\mathrm{cc1}}$ is the

@@

The calculations use different FF parametrizations which can lead to a $\sim$5.8 -6.6$\%$ variation of the theortical cross section.\\
%----REMOVED ON 10/14/2020----------
%The MS calculations used the FF parametrization of Ref. \cite{PhysRevC.70.068202} while the JML calculations used the conventional dipole parametrization for
%the proton and neutron magnetic FF, the Galster \cite{Galster:1971} parametrization
%for the neutron electric FF, and the results from the Hall A experiment of Ref. \cite{PhysRevLett.88.092301} for the proton electric FF parametrization.
%The JVO calculations used two different FF parametrizations (GKex05 \cite{PhysRevC.66.045501}, AMT \cite{PhysRevC.76.035205}) where a
%difference of $\sim5.8-6.6 \%$ was found between the respective
%JVO reduced cross sections. Figure \ref{fig:fig1} shows the results using only the GKex05 parametrization. \\

@@

  Insets: Blowup of the subfigures below $p_{\mathrm{r}}=$0.7 GeV/c.}

@@

%---include references that are not mentioned in the main text
%---but are included in the supplemental material
%---cite supp. material as follows:  (See Supplemental Material) after description of the topic being discussed.
%\nocite{COSY}
\nocite{barlow2002systematic}
\nocite{barlow2017}

### 2020-10-19 PRL_UTILITIES_CODES/supplementary_materials/latex_files/supp.tex
updated supp

energy cut around the deuteron binding energy ($\sim$2.2 MeV) using the missing energy formula described in the Letter, where the
recoiling system is assumed to be a neutron. The peak is not exactly at the deuteron binding energy because energy loss corrections have not
been applied to the data nor SIMC. Figure \ref{fig:Em_Q2_cuts} (right) shows a kinematical cut made on the 4-momentum transfer at $Q^{2} = 4.5\pm0.5$ (GeV/c)$^{2}$

@@

HMS can punch through the collimator with a probability that is related to the proton-Aluminum total cross section. Figure \ref{fig:data_coll_cuts} (right)

@@

acceptance is driven by that of the HMS. Figure \ref{fig:simc_coll_cuts} shows the same acceptance cuts as previously described, but for simulation.\\

@@

\includegraphics[scale=0.18]{plots/d2_kin_thnq35.png}

@@

\includegraphics[scale=0.18]{plots/d2_kin_thnq45.png}

@@

range. The integral over endcaps and $^{2}\mathrm{H}(e,e'p)n$ events show that the contribution from the cell walls is 0.00806/0.275 $\sim$ 0.0293 or approximately 2.9 $\%$
which is negligible.

@@

\section{\large Systematic Uncertainty Studies on Event Selection Cuts, Radiative and Bin-Centering Corrections }
A study of the sensitivity on the experimental cross section due to variations in the event selection cuts was carried out. 
To determine if the variation in each of the cuts contributes to a systematic effect and whether this contribution is significant
enough to be considered as a systematic error, we used the approach by R. Barlow described in Ref. \cite{barlow2002systematic}.\\
\indent Consider a cross section measurement done two different ways (i.e., apply different cuts). Let the measurements and their
statistical uncertainties be: ($\sigma^{\mathrm{exp}}_{\mathrm{1}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{1}}$) and ($\sigma^{\mathrm{exp}}_{\mathrm{2}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{2}}$)
where one of the measurements is a subset of the other. The difference and its associated uncertainty can be expressed as,
\begin{subequations}
  \begin{align}
    &\Delta \equiv \sigma^{\mathrm{exp}}_{\mathrm{1}} - \sigma^{\mathrm{exp}}_{\mathrm{2}}, \\
    &\sigma^{2}_{\Delta} \equiv (\delta\sigma^{\mathrm{exp}}_{\mathrm{1}})^{2} - (\delta\sigma^{\mathrm{exp}}_{\mathrm{2}})^{2},
  \end{align}
\end{subequations}
where the error of the difference between the two measurements is found by taking the difference of their variance. As demonstrated in Ref.\cite{barlow2002systematic}, this
error accounts for the possible correlation between the two measurements. By taking the ratio
\begin{equation}
  R_{\mathrm{Barlow}} \equiv \frac{\Delta}{\sigma_{\Delta}},
\end{equation}
a criterion imposed on $R_{\mathrm{Barlow}}$ determines whether the difference is significant enough to be considered as a systematic error or sufficiently small that it may be
ignored. This criterion requires knowledge of the correlation between the subsets, but in general, as suggested in Ref.\cite{barlow2017}: if $R_{\mathrm{Barlow}} < 2$ (or $\Delta <2\sigma_{\Delta}$)
the test passes and if $R_{\mathrm{Barlow}} > 4$ (or $\Delta >4\sigma_{\Delta}$), the test fails and the discrepancy must be added as a systematic error. For $2<R_{\mathrm{Barlow}}<4$, a judgement must be made.\\
\indent Figure \ref{fig:Em_sys} below shows an example of the systematic effects on the missing energy cut for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ over the full $p_{\mathrm{r}}$ range.
In Fig. \ref{fig:Em_sys}, the different color groups represent the Barlow ratio evaluated at difference between the subset and full missing energy cut range. For mostly the entire momentum range,
the Barlow ratio was kept within 2-4 standard deviations with the exception of a few outliers which can be understood from the fact that these might have very similar variances. These systematic
studies were mainly done to check the stability of the event selection cuts and the effects of cut variation on the cross section were found to be negligible. Similar plots for the other event selection
cuts systematics can be found in Section 5.10 of Ref. \cite{cyero_phdthesis}. 
\includegraphics[scale=0.4]{plots/Em_syst.png}
\caption{Systematic effects of the missing energy cut on the data cross section for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). The inner (black dashed) and outer (black solid)
  lines represent the $\Delta=\pm2\sigma_{\Delta}$ and $\pm4\sigma_{\Delta}$ boundaries, respectively.}
\label{fig:Em_sys}
\indent The systematic effect on the cross sections due to model dependency of the radiative and bin-centering corrections was investigated
using the Barlow ratio approach described above. In this case, the ratio was calculated from the difference between the experimental cross

@@

\includegraphics[scale=0.31]{plots/rad_sys.png}
\caption{Systematic effects of the radiative corrections model dependency on the data cross sections for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). The inner (black dashed) and outer (black solid) lines represent the $\Delta=\pm2\sigma_{\Delta}$ and $\pm4\sigma_{\Delta}$ boundaries, respectively.  }

@@

\includegraphics[scale=0.31]{plots/bc_sys.png}

@@

%\clearpage
\bibliography{supp}

>>>>

energy cut around the deuteron binding energy ($\sim$2.2 MeV) using the missing energy formula, $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$, where
$T_{p}$ is the final proton kinetic energy and $T_{\mathrm{r}}$ is the recoil particle kinetic energy which is calculated from the electron and proton
4-momentum vectors assuming an exclusive three-body final state with a recoiling neutron. The peak is not exactly at the deuteron binding energy because
energy loss corrections have not been applied to the data nor SIMC. \\
\indent Figure \ref{fig:Em_Q2_cuts} (right) shows a
kinematical cut made on the 4-momentum transfer at $Q^{2} = 4.5\pm0.5$ (GeV/c)$^{2}$

@@

HMS can punch through the collimator with a probability that is related to the proton-Tungsten total cross section. Figure \ref{fig:data_coll_cuts} (right)

@@

acceptance is driven by that of the HMS. Figure \ref{fig:simc_coll_cuts} shows the same acceptance cuts as previously described, but for simulation. The colored
$z$-axis in both figures is given in arbitrary units.\\

@@

\includegraphics[scale=0.17]{plots/d2_kin_thnq35.png}

@@

\includegraphics[scale=0.17]{plots/d2_kin_thnq45.png}

@@

range. The integral over endcaps and $^{2}\mathrm{H}(e,e'p)n$ events show that the contribution from the cell walls has an upper limit of 0.00806/0.275 $\sim$ 0.0293 or approximately 2.9 $\%$
as the integral was done over all recoil angles, $\theta_{nq}$. This result was added quadratically to the overall normalization error.

@@

\section{\large Systematic Uncertainty Studies on Radiative and Bin-Centering Corrections }
%\indent A study of the sensitivity on the experimental cross section due to variations in the event selection cuts was carried out. 
%To determine if the variation in each of the cuts contributes to a systematic effect and whether this contribution is significant
%enough to be considered as a systematic error, we used the approach by R. Barlow described in Ref. \cite{barlow2002systematic}.\\
%\indent Consider a cross section measurement done two different ways (i.e., apply different cuts). Let the measurements and their
%statistical uncertainties be: ($\sigma^{\mathrm{exp}}_{\mathrm{1}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{1}}$) and ($\sigma^{\mathrm{exp}}_{\mathrm{2}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{2}}$)
%where one of the measurements is a subset of the other. The difference and its associated uncertainty can be expressed as,
%\begin{subequations}
%  \begin{align}
%    &\Delta \equiv \sigma^{\mathrm{exp}}_{\mathrm{1}} - \sigma^{\mathrm{exp}}_{\mathrm{2}}, \\
%    &\sigma^{2}_{\Delta} \equiv (\delta\sigma^{\mathrm{exp}}_{\mathrm{1}})^{2} - (\delta\sigma^{\mathrm{exp}}_{\mathrm{2}})^{2},
%  \end{align}
%\end{subequations}
%where the error of the difference between the two measurements is found by taking the difference of their variance. As demonstrated in Ref.\cite{barlow2002systematic}, this
%error accounts for the possible correlation between the two measurements. By taking the ratio
%\begin{equation}
%  R_{\mathrm{Barlow}} \equiv \frac{\Delta}{\sigma_{\Delta}},
%\end{equation}
%a criterion imposed on $R_{\mathrm{Barlow}}$ determines whether the difference is significant enough to be considered as a systematic error or sufficiently small that it may be
%ignored. This criterion requires knowledge of the correlation between the subsets, but in general, as suggested in Ref.\cite{barlow2017}: if $R_{\mathrm{Barlow}} < 2$ (or $\Delta <2\sigma_{\Delta}$)
%the test passes and if $R_{\mathrm{Barlow}} > 4$ (or $\Delta >4\sigma_{\Delta}$), the test fails and the discrepancy must be added as a systematic error. For $2<R_{\mathrm{Barlow}}<4$, a judgement must be made.\\
%\indent Figure \ref{fig:Em_sys} below shows an example of the systematic effects on the missing energy cut for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ over the full $p_{\mathrm{r}}$ range.
%In Fig. \ref{fig:Em_sys}, the different color groups represent the Barlow ratio evaluated at difference between the subset and full missing energy cut range. For mostly the entire momentum range,
%the Barlow ratio was kept within 2-4 standard deviations with the exception of a few outliers which can be understood from the fact that these might have very similar variances. These systematic
%studies were mainly done to check the stability of the event selection cuts and the effects of cut variation on the cross section were found to be negligible. Similar plots for the other event selection
%cuts systematics can be found in Section 5.10 of Ref. \cite{cyero_phdthesis}. 
%\clearpage
%\begin{figure}[!ht]
%\includegraphics[scale=0.4]{plots/Em_syst.png}
%\caption{Systematic effects of the missing energy cut on the data cross section for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). The inner (black dashed) and outer (black solid)
%  lines represent the $\Delta=\pm2\sigma_{\Delta}$ and $\pm4\sigma_{\Delta}$ boundaries, respectively.}
%\label{fig:Em_sys}
%\end{figure}
\indent The systematic effect on the cross sections due to model dependency of the radiative and bin-centering corrections was investigated (see Section 5.10 of Ref.\cite{cyero_phdthesis})
using the Barlow ratio approach \cite{barlow2002systematic,barlow2017}. In this case, the ratio was calculated from the difference between the experimental cross

@@

\includegraphics[scale=0.37]{plots/rad_sys.png}
\caption{Systematic effects of the radiative corrections model dependency on the data cross sections
  for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). The inner (black dashed) and outer (black solid)
  lines represent the $\Delta=\pm2\sigma_{\Delta}$ and $\pm4\sigma_{\Delta}$ boundaries, respectively.  }

@@

\includegraphics[scale=0.37]{plots/bc_sys.png}

@@

\indent Systematic studies of the event selection cuts described above were also carried out using the R. Barlow approach. The studies demonstrated that variations in the software had a negligible
effect in the measured cross sections and thus no systematic uncertainties due to software cuts were included in the final result. For a detailed discussion of these studies see Section 5.10 of Ref.\cite{cyero_phdthesis}.
\\\\
\bibliography{supp}
